Bayesian estimation of chronic disease epidemiology from incomplete data

### 2018-06-26 vignette.Rmd
fix stan link

First load Stan and its R interface, after installing it into R if necessary with `install.packages("rstan")`. 
```{r,message=FALSE}
library(rstan)
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)
```
In this example, the theoretical disease model, statistical model and priors are written down in Stan language in the file [gbdcf-unsmoothed.stan](gbdcf-unsmoothed.stan).

>>>>

First load Stan and its R interface, after installing it into R if necessary with `install.packages("rstan")`. 
```{r,message=FALSE}
library(rstan)
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)
```
In this example, the theoretical disease model, statistical model and priors are written down in Stan language in the file [gbdcf-unsmoothed.stan](https://github.com/chjackson/disbayes/blob/master/gbdcf-unsmoothed.stan).
